Streaming Slot-Value Extraction for Wikipedia Entities at Web-Scale

### 2013-11-14 paper/flairs27/content/conclusion.tex
added a conclusion section

%\section{Conclusions}

>>>>

\section{Conclusions}

In this paper we described an approach to perform fact extraction over one of the largest data sets to date. 
We generate aliases for Wikipedia entities using an API and extract some aliases from Wikipedia pages text itself.
We process documents that mention entities for slot value extraction.
Slot values are determined using pattern matching over tagged entities in sentences.
Finally post processing will filter, cleanup and infers some new slot values to enhance recall and accuracy.

We sampled documents from the training data period to generate an initial set of patterns and then use these patterns to generate results.
After manually examining the results, we prune patterns with poor performance and add patterns that may add to extraction coverage.
We use several iterations to find the best patterns.
%We found that it is very time consuming to identify quality patterns.

%We noticed that some tools that claim to be performant for using the hardware capabilities at hand sometimes don't really work as claimed and you should not always rely on one without a thorough A/B testing of performance which we ended up in generating our in-house system for processing the corpus and passing through the filter. Furthermore, on extracting slot values, pattern matching might not be the best options but definitely can produce some good results at hand. We have plans on generating classifiers for slot value extraction purposes. Entity resolution on the other hand was a topic we spent sometime on but could not get to stable grounds for it. Entity resolution will distinguish between entities of the same name but different contexts. Further improvements on this component of the system are required.

We look to continue exploration of streaming extraction models over this large data set.
Our models are simple and provide a great baseline framework to develop and compare innovative techniques.

### 2013-11-14 paper/flairs27/content/discussion.tex
made updates after morteza. we need to cut the paper down to 6 pages
added a conclusion section

\section{Discussions}

@@

Some of the entities are popular and appear at a greater frequency in the data set.
For example, a `Corn Belt Power Cooperative' Google search results in 86,800 documents, where as `William H. Gates' returns 3,880,000 documents. 
%\ceg{Add an example of someone who is either much larger of smaller.}
We observed that more than half of the entities have appeared in less than 10 documents.
%\ceg{Can we add this figure - } 
A large portion have appeared only once. This magnificient change in coverage support the viability of our seach and filter schemes.

@@

In this paper we described an approach to perform fact extraction over one of the largest data sets to date. 
We generate aliases for Wikipedia entities using an API and extract some aliases from Wikipedia pages text itself.
We process documents that mention entities for slot value extraction.
Slot values are determined using pattern matching over coreferences of entities in sentences. Finally post processing will filter, cleanup and infers some new slot values to enhance recall and accuracy.

We sampled documents from the training data period to generate an initial set of patterns and then use these patterns to generate results.
After manually examining the results, we prune patterns with poor performance and add patterns that may add to extraction coverage.
We use several iterations to find the best patterns.
%We found that it is very time consuming to identify quality patterns.

%We noticed that some tools that claim to be performant for using the hardware capabilities at hand sometimes don't really work as claimed and you should not always rely on one without a thorough A/B testing of performance which we ended up in generating our in-house system for processing the corpus and passing through the filter. Furthermore, on extracting slot values, pattern matching might not be the best options but definitely can produce some good results at hand. We have plans on generating classifiers for slot value extraction purposes. Entity resolution on the other hand was a topic we spent sometime on but could not get to stable grounds for it. Entity resolution will distinguish between entities of the same name but different contexts. Further improvements on this component of the system are required.

We look to continue exploration of streaming extraction models over this large data set.
Our models are simple and provide a great baseline framework to develop and compare innovative techniques.

>>>>

\section{Discussion}

@@

Some of the entities are popular and appear at a greater frequency in the data set.
For example, a `Corn Belt Power Cooperative' Google search results in 86,800 documents, where as `William H. Gates' returns 3,880,000 documents. 
%\ceg{Add an example of someone who is either much larger of smaller.}
We observed that more than half of the entities appear in less than 10 documents in the data set;
%\ceg{Can we add this figure - } 
a large portion have appeared only once. This magnificient change in coverage support the viability of our seach and filter schemes.

@@
